{\LARGE {\color{red}PLACEHOLDER-TITLE:} Functional Linear Regression in a Scalar-on-Function Setting with Applications to SOMETHING}

### 2021-12-16 main.tex
Karhunen-Loeve stuff

	\subsection{Karhunen-Lo\'{e}ve Expansion and Empirical Eigenbases}
	Given a set of i.i.d. functional observations, it is possible to represent them in terms of their generating stochastic process.

>>>>

	\subsection{Karhunen-Lo\'{e}ve Expansion and Empirical Eigenbases}
	Given a realization of a random function realizing in $\mathbb{L}^2$, it is possible to represent this realization in terms of its generating stochastic process. To motivate it, it is necessary to define the covariance function of a random function realizing in $\mathbb{L}^2$. Therefore, let $F: \Omega \mapsto \mathbb{L}^2[0,1]$ be such a random function.
	Then the mean and covariance functions of $F$ are defined as follows.

	\begin{equation}\label{MeanFunction}
		\mu(t) = \mathbb{E}\left[ F(\omega)(t) \right]
	\end{equation}

	\begin{equation}\label{CovarianceFunction}
		c(t,s) = \mathbb{E}\big[ \left( F(\omega)(t) - \mu(t) \right) \left( F(\omega)(s) - \mu(s) \right) \big]
	\end{equation}

	Theoretical considerations lead to the result that $F$ can be represented in the following form, called its Karhunen-Lo\'{e}ve expansion.

	\begin{equation}\label{KarhunenLoeve}
		F(\omega)(t) = \mu(t) + \sum_{j = 1}^{\infty} \xi_j(\omega) \nu_j(t)
	\end{equation}

	where the $\nu_j$ are defined by the countable set of solutions $\{(\lambda_i, \nu_i) \: \vert \: i \in \mathcal{I}\}$ of the following equation.

	\begin{equation}
		\int_{0}^{1}c(t,s)\nu(s) \mathrm{d}s = \lambda \nu(t)
	\end{equation}

	The $\xi_j(\omega)$ are then given as $\xi_j(\omega) = \langle F(\omega) - \mu, \nu_j\rangle$ and thereby random variables realizing in $\mathbb{R}$.

	In the typical scalar setting, a similar consideration leads to the concept of principal components. This is also possible in a functional setting. Let $\{f_1(t), \dots, f_n(t)\}$ be a set of i.i.d. realizations generated by a random function $F(\omega) \mapsto \mathbb{L}^2[0,1]$.
	Define the following sample analogues for the mean and covariance functions.

	\begin{equation}
		\hat{\mu}(t) = \frac{1}{n}\sum_{j = 1}^{n}f_j(t)
	\end{equation}

	\begin{equation}
		\hat{c}(t,s) = \frac{1}{n} \sum_{j = 1}^{n} \left(f_j(t) - \hat{\mu}(t)\right) \left(f_j(s) - \hat{\mu}(s)\right)
	\end{equation}

	With these it is possible to derive a set of sample analogs $\{(\hat{\lambda}_i, \hat{\nu}_i) \: \vert \: i \in \mathcal{I}\}$ for $\{(\lambda_i, \nu_i) \: \vert \: i \in \mathcal{I}\}$ as the solutions of the following equation. {\color{red} I think the number of principal components has to be smaller then the number of observations. So I can give more information about $\mathcal{I}$.}

	\begin{equation}
		\int_{0}^{1}\hat{c}(t,s)\hat{\nu}(s) \mathrm{d}s = \hat{\lambda} \hat{\nu}(t)
	\end{equation}

	This naturally leads to the following representation.

	\begin{equation}
		f_i(t) = \sum_{j = 1}^{{\color{red} !!!}} \hat{\xi}_{i,j} \hat{\nu}(t)
	\end{equation}

	\subsection{Generating Similar Curves}
